---
title: "math4753 Lab Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{math4753 Lab Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(package1)
```

# Introduction

This package contains various of packages made and used in the University of Oklahoma's MATH 4753 course. The functions are listed and described below.

# Functions

## binx()

The binx() function creates a barplot of successes in a binomial experiment

```{r}
a = binx(n = 20, iter = 10000, p = 0.25)
```

## myclt()

The myclt() function creates a random sample and uses it to make a histogram. The function conforms to the central limit theorem.

```{r}
b = myclt(10, 10000)
```

## myncurve()

The myncurve() function creates a normal probability distribution.

```{r}
c = myncurve(5, 20, 0.5)
```

## rf.hist()

The rf.hist() function creates a Relative Frequency Histogram using data from a given vector.

```{r}
f = fire$DAMAGE
d = rf.hist(f, bins = 8)
```

